Using Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2020-12-10 thesis/thesis.tex
thesis: Add Melotte 25 results

% TODO: Exposición de resultados y comentarios
% Es una exposición objetiva, sin valorar los resultados ni justificarlos.

>>>>

\subsection{Melotte 25}

\begin{figure}[H]
  \vfil
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/pm_melotte_25.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/parallax_melotte_25.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/hr_diagram_melotte_25.png}
    \end{subfigure}
  \end{subfigure}
  \caption{Melotte 25 Clusterix+TOPCAT characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/kmeans_pm_melotte_25.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/kmeans_parallax_melotte_25.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/kmeans_hr_diagram_melotte_25.png}
    \end{subfigure}
  \end{subfigure}
  \caption{Melotte 25 KMeans characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_pm_melotte_25.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_parallax_melotte_25.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_hr_diagram_melotte_25.png}
    \end{subfigure}
  \end{subfigure}
  \caption{Melotte 25 DEC characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_pm_filtered_melotte_25.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_parallax_filtered_melotte_25.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_hr_diagram_filtered_melotte_25.png}
    \end{subfigure}
  \end{subfigure}
  \caption{Melotte 25 DEC (filtered) characterization.}
\end{figure}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 11 \\
      Clustering Layer & $\left[ 50, 50, 80 \right]$ \\
      Kernel Initializer Seed & 11 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{Melotte 25 DEC model hyperparameters.}
    \label{tab:hyperparameters_melotte_25}
  \end{center}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \textbf{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \textbf{$\mu_{\delta}$ $(mas/yr^{-1})$} & \textbf{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & 104.92 $\pm$ 0.12 & -28.00 $\pm$ 0.09 & 21.052 $\pm$ 0.065 & - \\
      Clusterix+TOPCAT & 106.796 $\pm$ 6.229 & -24.870 $\pm$ 5.417 & 21.210 $\pm$ 1.115 & 109 \\
      KMeans & 81.410 $\pm$ 71.475 & -45.309 $\pm$ 73.945 & 21.056 $\pm$ 6.018 & 365 \\
      DEC & x $\pm$ x & x $\pm$ x & x $\pm$ x & x \\
      \textbf{DEC (filtered)} & x $\pm$ x & x $\pm$ x & x $\pm$ x & x \\
    \end{tabular}
    \caption{Melotte 25 results.}
    \label{tab:results_melotte_25}
  \end{center}
\end{table}
